How unprecedented was the February 2021 Texas cold snap?

### 2021-02-28 doc/article.tex
Add zenodo DOI

We are committed to open science.
Our open source code is freely available in a live repository at \url{https://github.com/jdossgollin/2021-TXtreme} and in an archived repository at TODO.
Reproducibility is facilitated through the Snakemake library \cite{koster_snakemake:2012}.

>>>>

We are committed to open science.
Our open source code is freely available in a live repository at \url{https://github.com/jdossgollin/2021-TXtreme} and in an archived repository at \url{https://dx.doi.org/10.5281/zenodo.4568923}.
Reproducibility is facilitated through the Snakemake library \cite{koster_snakemake:2012}.
